Interactive Curvature Tensor Visualization on Digital Surfaces\thanks{This work has been mainly funded by \textsc{DigitalSnow} ANR-11-BS02-009, \textsc{KIDICO} ANR-2010-BLAN-0205 and \textsc{PRIMES Labex} ANR-11-LABX-0063/ ANR-11-IDEX-0007 research grants.}

### 2015-10-23 latex/article.tex
figs

We first evaluate the curvature estimation on a full-resolution
geometry obtained by disabling the LoD criterion at the mesh
generation step. We compare the approximation made to accelerate
visualisation with the ground truth result obtained at level $l_0$.
We also compare it with the hierarchical algorithm.
The results are presented table \ref{tab:full-res-stat}, and illustrated
figure \ref{fig:refine}. For all illustrations, we use directly normal vectors computed by algorithm
discussed in Section~\ref{sec:curv-tens-estim}

@@

\begin{figure}
  \begin{center}
    {\includegraphics[width=2.7cm]{figs/EG_dragon_mean}}
    {\includegraphics[width=2.7cm]{figs/EG_dragon_gaussian}}
    {\includegraphics[height=2.0cm]{figs/EG_dragon_dir_min_zoom}}
    {\includegraphics[height=2.0cm]{figs/EG_dragon_dir_max_zoom}}\\
    % {\includegraphics[height=4.0cm]{figs/EG_dragon_normal_zoom}}
    {\includegraphics[height=4.0cm]{figs/xyzrgb_dragon-510_R8_mean}}
    {\includegraphics[height=3.5cm]{figs/snow_I08iso_233_r20_l0_m3}}\\
    {\includegraphics[width=2.2cm]{figs/function_mean_0}}
    {\includegraphics[width=2.2cm]{figs/function_mean_1}}
    {\includegraphics[width=2.2cm]{figs/function_mean_2}}
    {\includegraphics[width=2.2cm]{figs/function_mean_3}}
    {\includegraphics[width=2.2cm]{figs/function_mean_4}}
  \end{center}
  \caption{Illustration fig illustration complete (adaptative, ...) plusieurs
    objets.. + dynamique.
    Illustration of mean curvature computation of snow microstructures.
    %
    \emph{Third row:} mean curvature computed in real-time on a dynamic object.}
  \label{fig:full}
\end{figure}

>>>>

\begin{figure}
  \begin{center}
    {\includegraphics[width=2.7cm]{figs/Octa_mean}}
    {\includegraphics[width=2.7cm]{figs/Octa_gaussian}}
    {\includegraphics[width=2.7cm]{figs/Octa_k1}}
    {\includegraphics[width=2.7cm]{figs/Octa_k2}}\\
    {\includegraphics[width=2.7cm]{figs/Octa_dir_min}}
    {\includegraphics[width=2.7cm]{figs/Octa_dir_max}}
    {\includegraphics[height=2.5cm]{figs/Octa_dir_min_zoom}}
    {\includegraphics[height=2.5cm]{figs/Octa_dir_max_zoom}}\\
    % {\includegraphics[height=4.0cm]{figs/EG_dragon_normal_zoom}}
    {\includegraphics[width=2.2cm]{figs/function_mean_0}}
    {\includegraphics[width=2.2cm]{figs/function_mean_1}}
    {\includegraphics[width=2.2cm]{figs/function_mean_2}}
    {\includegraphics[width=2.2cm]{figs/function_mean_3}}
    {\includegraphics[width=2.2cm]{figs/function_mean_4}}
  \end{center}
  \caption{Illustration fig illustration complete (adaptative, ...) plusieurs
    objets.. + dynamique.
    Illustration of mean curvature computation of snow microstructures.
    %
    \emph{Third row:} mean curvature computed in real-time on a dynamic object.}
  \label{fig:full}
\end{figure}

We first evaluate the curvature estimation on a full-resolution geometry
obtained by disabling the LoD criterion at the mesh generation step.
Figure~\ref{fig:full}-top and middle show results of curvature tensor estimation
(mean, Gaussian curvature, first and second principal curvatures, first and
second principal directions) on an OctaFlower. Figure~\ref{fig:full}-bottom
shows the mean curvature estimation in real-time on a dynamic object.

We compare the approximation made to accelerate
visualisation with the ground truth result obtained at level $l_0$.
We also compare it with the hierarchical algorithm.
The results are presented table \ref{tab:full-res-stat}, and illustrated
figure \ref{fig:refine}. For all illustrations, we use directly normal vectors computed by algorithm
discussed in Section~\ref{sec:curv-tens-estim}

@@

\begin{figure}
  \begin{center}
    {\includegraphics[height=4.0cm]{figs/xyzrgb_dragon-510_R8_mean}}
    {\includegraphics[height=3.5cm]{figs/snow_I08iso_233_r20_l0_m3}}
  \end{center}
  \caption{Illustration fig illustration complete (adaptative, ...) plusieurs
    objets.. + dynamique.
    Illustration of mean curvature computation of snow microstructures.
    %
    \emph{Third row:} mean curvature computed in real-time on a dynamic object.}
  \label{fig:adaptive}
\end{figure}
